Graph-Based Neural Reconstruction \\ from Skeletonized 3D Networks

### 2017-11-16 papers/cvpr2018/1_related_work.tex
Removed Fig. 2
final edit pass

% !TEX root =  paper.tex
\section{Related Work}

We review some of the most successful segmentation methods that have been applied to large-scale EM images in connectomics. Fig.~\ref{fig:pipeline} shows the results of a typical connectomics segmentation pipeline.

@@

\paragraph{Error-correction methods.}
Some recent research builds on top of these region-based methods to correct errors in the segmentation either using human proofreading~\cite{raveler,mojo2,haehn_dojo_2014,haehn2017guided} or fully automatically~\cite{rolnick2017morphological,error_correction_using_CNN}.
However, to our knowledge, our method is the first to extract a 3D graph from pixel-based segmentations for a true top-down error correction approach. This allows us to enforce domain-specific biology constraints and efficient graph partitioning algorithms. Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
Even though graph partitioning is an NP-Hard problem~\cite{demaine2006correlation} there are several useful multicut heuristics that provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis}. We use the method of Keuper et al.~\cite{keuper2015efficient} to partition the extracted 3D graph into the final neural reconstruction.

>>>>

% !TEX root =  paper.tex

\section{Related Work}

We review some of the most successful segmentation methods that have been applied to large-scale EM images in connectomics.
%Fig.~\ref{fig:pipeline} shows the results of a typical connectomics segmentation pipeline.

@@

\paragraph{Error-correction methods.}
Some recent research builds on top of these region-based methods to correct errors in the segmentation either using human proofreading~\cite{mojo2,haehn2014design,haehn2017guided} or fully automatically~\cite{rolnick2017morphological,error_correction_using_CNN}.
However, to our knowledge, our method is the first to extract a 3D graph from pixel-based segmentations for a true top-down error correction approach. This allows us to enforce domain-specific biology constraints and efficient graph partitioning algorithms. Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
Even though graph partitioning is an NP-Hard problem~\cite{demaine2006correlation} there are several useful multicut heuristics that provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis}. We use the method of Keuper et al.~\cite{keuper2015efficient} to partition the extracted 3D graph into the final neural reconstruction.

### 2017-11-16 papers/cvpr2018/2_method.tex
final edit pass

\begin{figure*}[t!]
	\begin{center}
	\includegraphics[width=0.24\linewidth]{./figures/methods/multicut_input.png}
	\includegraphics[width=0.24\linewidth]{./figures/methods/pre-multicut.png}
	\includegraphics[width=0.24\linewidth]{./figures/methods/multicut-graph.png}
	\includegraphics[width=0.24\linewidth]{./figures/methods/post-multicut.png}
	\end{center}
	\caption{Overview of the proposed methods.}
	\label{fig:overview}
\end{figure*}

\begin{figure}[t]
	\centering
	\includegraphics[width=0.92\linewidth]{./figures/skeleton1.png}
	\includegraphics[width=0.92\linewidth]{./figures/skeleton2.png}
	\caption{Example skeletons (in black) extracted from segments (blue and green) using the TEASER algorithm.}
	\label{fig:skeletonization}
\end{figure}

@@

From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with non-negative edge weights $w_e$. The nodes correspond to label segments from the segmentation with edges between segments considered for merging. Ideally, our graph has edges corresponding to all of the segments that were erroneously split. To compute this graph we generate a skeleton for every segment in the pixel-based segmentation. The skeletonized 3D network is a simplified representation of the overall branching structure of the neurons. From these skeletons we identify potential merge locations and produce the corresponding edges for the graph. To find actual merges we run a classification CNN to generate edge weights corresponding to merge probabilities. We then use a multicut algorithm to generate a partition on the graph where nodes in the same partition are assigned the same output label in the improved segmentation. We will now discuss the three major components to our framework (graph creation, edge weights assignment, and graph partitioning) in more detail.

>>>>

\begin{figure*}[htbp]
	\begin{center}
	\includegraphics[width=0.24\linewidth]{./figures/methods/multicut_input.png}
	\includegraphics[width=0.24\linewidth]{./figures/methods/pre-multicut.png}
	\includegraphics[width=0.24\linewidth]{./figures/methods/multicut-graph.png}
	\includegraphics[width=0.24\linewidth]{./figures/methods/post-multicut.png}
	\end{center}
	\caption{Outline of our approach, from left to right: Result of the pixel-based segmentation and agglomeration algorithm; segments of several selected neurons from the initial segmentation; extracted skeletonized 3D network of those segments; improved 3D reconstruction of the selected segments after graph construction and partitioning with constraints.}
	\label{fig:overview}
\end{figure*}

\begin{figure}[t]
	\centering
	\includegraphics[width=0.92\linewidth]{./figures/skeleton1.png}
	\includegraphics[width=0.92\linewidth]{./figures/skeleton2.png}
	\caption{Example skeletons (in black) extracted from segments (blue and green) using the TEASER algorithm. \hp{there is enough space to add another example in this figure}}
	\label{fig:skeletonization}
\end{figure}

@@

From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with non-negative edge weights $w_e$. The nodes correspond to label segments from the segmentation with edges between segments considered for merging. Ideally, our graph has edges corresponding to all of the segments that were erroneously split. To compute this graph we generate a skeleton for every segment in the pixel-based segmentation (Fig.~\ref{fig:overview}). The skeletonized 3D network is a simplified representation of the overall branching structure of the neurons. From these skeletons we identify potential merge locations and produce the corresponding edges for the graph. To find actual merges we run a classification CNN to generate edge weights corresponding to merge probabilities. We then use a multicut algorithm to generate a partition on the graph where nodes in the same partition are assigned the same output label in the improved segmentation. We will now discuss the three major components to our framework (graph creation, edge weights assignment, and graph partitioning) in more detail.
